State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-22 paper/chapters/4_classification.tex
paper: add formular for SVM
Paper: Features

The characteristics of twitter messages introduce further challenges. Due to the structure of these messages, sentiment analysis of tweets is different from analysing conventional texts, such as review documents, in various ways. The length of at most 140 characters and the rather informal spelling style pose problems that have to be considered carefully when analysing the data. When preprocessing the texts these aspects already need to be handled so that the actual classification process is supplied with information that is considered useful for the analysis phase. After this step it is necessary to collect the relevant information as so called \emph{features} and organize them into a \emph{feature vector}.

\subsection{Features}

@@

>>>>

The characteristics of twitter messages introduce further challenges. Due to the structure of these messages, sentiment analysis of tweets is different from analyzing conventional texts, such as review documents, in various ways. The length of at most 140 characters and the rather informal spelling style pose problems that have to be considered carefully when analyzing the data. When preprocessing the texts these aspects already need to be handled so that the actual classification process is supplied with information that is considered useful for the analysis phase. After this step it is necessary to collect the relevant information as so called \emph{features} and organize them into a \emph{feature vector}.

\subsection{Features}
As twitter messages are composed of an arbitrary number of words makes it necessary to extract exactly those words which preferably describes the characteristics of such tweets. Extracting those words to an object by making use of various word selecting techniques is called a feature vector. These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exists. 
	\emph{Term Presence} is a method where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present". A similar approach is to count the number of occurred words in a message and use the numeric value as a feature, which is called \emph{Term Frequency} but Pang et al. showed \autocite{Pang2008} that Term Presence performed better compared to Term Frequency.
TODO

@@

\begin{equation*}
\vec{\omega} := \sum_j \alpha_j c_j \vec{d}_j,\quad \alpha_j \geq 0
\end{equation*}
